\documentclass[10pt]{book}

\usepackage{times}
\usepackage{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{tabularx}

\setstretch{1.2}
\newgeometry{left=0.5in, right=0.5in, top=0.5in, bottom=0.5in}

\author{David McLain}

\begin{document}
    {
        \fontfamily{ptm}
        \selectfont
        \pagenumbering{gobble}
        % Header for resume
        {\centering
            % Name
            {
                \fontsize{13}{13}
                \selectfont David McLain
                \\
            }
            % Email, portfolio, linkedin
            {
                \fontsize{12}{12}
                \selectfont
                \href{mailto:davidmclain@arizona.edu}{davidmclain@arizona.edu}
                \\
                \href{https://david-mclain.github.io/}{https://david-mclain.github.io/}
                \hspace{1pt}\textbar\hspace{1pt}
                \href{https://www.linkedin.com/in/mclain-david}{https://www.linkedin.com/in/mclain-david}
                \\
            }
        }
        % Education Section
        % Header for Education
        \begin{spacing}{0.2}
            \noindent\fontsize{12}{12}
            \selectfont\hspace{-3pt}\textbf{EDUCATION}
            \\
            \rule{\linewidth}{0.4pt}
            \\
            \\
            \\
            \\
        \end{spacing}
        % School Name with Major (UofA)
        {
            \fontsize{11}{11}
            \selectfont
            \noindent\textbf{University of Arizona}\hfill Tucson, Arizona
            \\
            \textbf{\textit{Bachelor of Science, Computer Science}}\hfill May 2021\hspace{3pt}\textendash\hspace{3pt}Present
            \\
        }
        % Achievements
        \textit{Minor in Mathematics}
        \\
        \hspace{2pt}-\hspace{6pt}GPA: 3.6 / 4.0
        \\
        \hspace{2pt}-\hspace{6pt}ASEMS NSF Grant Scholarship
        \\
        % School Name with Major (Pima)
        {
            \fontsize{11}{11}
            \selectfont
            \noindent\textbf{Pima Community College}\hfill Tucson, Arizona
            \\
            \textbf{\textit{Pre-Engineering}}\hfill August 2019\hspace{3pt}\textendash\hspace{3pt}May 2021
            \\
        }
        \vspace{-\baselineskip}\vspace{-\parskip}
        % Skills Section
        % Header for Skills
        \begin{spacing}{0.2}
            {
                \noindent\fontsize{12}{12}
                \\
                \\
                \selectfont\textbf{TECHNICAL SKILLS}
                \\
            }
            \rule{\linewidth}{0.4pt}
            \\
            \\
            \\
            \\
        \end{spacing}
        % Skills here
        \noindent
        Programming Languages: Java; Python; C\#; C; MIPS; SQL; Bash; JavaScript; HTML; CSS
        \\
        Operating Systems: Linux; Unix; Windows
        \\
        Software and Libraries: Git; Vim; Lucene; Pandas; NumPy; Make
        % Experience Section
        % Header for Experience
        \begin{spacing}{0.2}
            {
                \noindent\fontsize{12}{12}
                \\
                \\
                \selectfont\textbf{RELEVANT EXPERIENCE}
                \\
            }
            \rule{\linewidth}{0.4pt}
            \\
            \\
            \\
            \\
        \end{spacing}
        % RA Information
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{Department of Aerospace and Mechanical Engineering, University of Arizona \textendash}
            \hfill June 2023\hspace{3pt}\textendash\hspace{3pt}Present
        }
        \\
        \textit{Undergraduate Research Assistant}
        \\
        \hspace{2pt}-\hspace{6pt}Designing and implementing wrapper classes to automate simulation tasks 
        while seamlessly integrating machine learning algorithms for advanced data analysis.
        \\
        \hspace{2pt}-\hspace{6pt}Translating complex MATLAB codebase to Python libraries, incorporating 
        machine learning frameworks such as TensorFlow and scikit-learn for data-driven decision-making.
        \\
        \hspace{2pt}-\hspace{6pt}Operating within an agile development framework, participating in weekly 
        sprint planning, stand-up, and retrospective meetings to track progress, address challenges, and 
        ensure timely delivery of projects and milestones.
        \\
        % TA Information
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{University of Arizona, Department of Computer Science \textendash}
            \hfill December 2022\hspace{3pt}\textendash\hspace{3pt}Present
        }
        \\
        \textit{Undergraduate Course Coordinator}
        \\
        \hspace{2pt}-\hspace{6pt}Serving as an undergraduate Course Coordinator in Computer Architecture, 
        providing academic support to students by hosting weekly office hours to provide students with 
        additional opportunities to practice course concepts, and receive personalized feedback.
        \\
        \hspace{2pt}-\hspace{6pt}Collaborating with the course instructor and other teaching assistants to 
        ensure consistency in teaching style, grading policies, and course content.
        % Projects Section
        % Header for Projects
        \begin{spacing}{0.2}
            {
                \noindent\fontsize{12}{12}
                \\
                \\
                \selectfont\textbf{PROJECTS}
                \\
            }
            \rule{\linewidth}{0.4pt}
            \\
            \\
            \\
            \\
        \end{spacing}
        % Operating System
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{Operating System \textendash}\hfill In Progress
        }
        \\
        \hspace{2pt}-\hspace{6pt}Collaborating with a partner to design and develop a custom operating system from scratch in C.
        \\
        \hspace{2pt}-\hspace{6pt}Implemented critical foundational components of the operating system, including 
        bootloading, process table management, and process lifecycle control.
        \\
        \hspace{2pt}-\hspace{6pt}Designed and implemented a robust process dispatcher that efficiently schedules 
        and manages system tasks and user processes, incorporating a round-robin scheduling algorithm with an 80 
        ms quantum time slice, ensuring fair and predictable task execution.
        \\
        % MiniWatson
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{Mini Watson \textendash}\hfill Spring 2023
        }
        \\
        \hspace{2pt}-\hspace{6pt}Led a team of 5 developers in the creation of a software application 
        that acted as a simplified version of IBM's Watson Question Answering machine.
        \\
        \hspace{2pt}-\hspace{6pt}Developed the application using Java, and integrated OpenNLP and Lucene 
        frameworks to implement a bag of words and probabilistic model for searching indexed Wikipedia documents.
        \\
        \hspace{2pt}-\hspace{6pt}Coordinated with team members to design and implement an algorithm that 
        indexed relevant Wikipedia documents and extracted necessary information using natural language processing techniques.
        \\
        % Chess
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{Chess Game \textendash}\hfill Fall 2022
        }
        \\
        \hspace{2pt}-\hspace{6pt}Managed a team of 4 developers in the development of a GUI-based chess application 
        using Java's Swing and AWT libraries, which included features such as online gameplay, saving and loading games, 
        and a competitive mode.
        \\
        \hspace{2pt}-\hspace{6pt}Implemented agile development methodologies to ensure efficient and flexible project 
        management, including regular team meetings, task prioritization, and continuous integration and deployment.
        \\
        \hspace{2pt}-\hspace{6pt}Utilized object-oriented design patterns such as the Model-View-Controller (MVC) 
        pattern to develop a and user-friendly interface.
        \iffalse
        \\
        % Sorting Algorithm Visualizer
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{Sorting Algorithm Visualizer \textendash}\hfill Winter 2022
        }
        \\
        \hspace{2pt}-\hspace{6pt}Designed and implemented a sorting algorithm visualizer using Javascript, 
        HTML, and CSS to showcase the functionality of merge sort, quicksort, and heapsort algorithms.
        \\
        \hspace{2pt}-\hspace{6pt}Used HTML and CSS to create an engaging and user-friendly interface that 
        displayed the array of numbers and highlighted the current step in the sorting process.
        \\
        \hspace{2pt}-\hspace{6pt}Demonstrated proficiency in software development, algorithm design, and 
        web development by delivering a high-quality project that received positive feedback from users.
        \\
        % Text Editor
        {
            \noindent\fontsize{11}{11}
            \selectfont\hspace{-3pt}\textbf{Text Editor \textendash}\hfill Fall 2022
        }
        \\
        \hspace{2pt}-\hspace{6pt}Led a team of two developers in the successful design, development, and 
        deployment of a feature-rich text editor application.
        \\
        \hspace{2pt}-\hspace{6pt}Spearheaded the incorporation of the composite design pattern into the 
        application's structure, allowing for the seamless composition of complex document structures from simple elements.
        \\
        \hspace{2pt}-\hspace{6pt}Managed the integration of key features, including rich text formatting, 
        undo/redo functionality, and file management, while maintaining a user-friendly interface.
        \\
        \hspace{2pt}-\hspace{6pt}Employed AWT's native peer components to seamlessly integrate with the 
        underlying platform, providing a consistent look and feel for users accustomed to their respective operating systems.
        \fi
        \iffalse
        % Coursework Section
        % Coursework Header
        \begin{spacing}{0.2}
            {
                \noindent\fontsize{12}{12}
                \\
                \\
                \selectfont\textbf{RELEVANT COURSEWORK}
                \\
            }
            \rule{\linewidth}{0.4pt}
            \\
            \\
            \\
            \\
            \\
        \end{spacing}
        \noindent
        \begin{tabular}{p{0.5\textwidth} p{0.5\textwidth}}
            Object-Oriented Programming and Design & Data Structures and Algorithms \\
            Cloud Computing & Operating Systems (In Progress) \\
            Principles of Data Science & Systems Programming \& UNIX \\
            % Database Design & Systems Programming \& UNIX \\
            %Text Retrieval \& Web Search & Software Development \\
        \end{tabular}
        \fi
    }
\end{document}
